Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-14 extended_catalog/paper/extended_catalog.tex
lots of markus suggestions

\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}
\usepackage[toc,page]{appendix}

@@

@@

For each of these sources, the extension was determined based on
dedicated analysis of the particular source or region of interest
instead of being the outcome of a systematic search of the LAT catalog.
For the systematic scan of all LAT catalog sources presented here, we
therefore expect to find additional spatially extended LAT sources, in
particular since many extended sources in the Galactic plane have been
detected at \tev energies using Air Cherenkov detectors and \tev and
\gev emission often originates from the same population of high-energy
particles.  A variety of spatially extended sources have been detected
in the Galactic plane at \tev energies. Most prominent was a survey of
the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
which presented 14 spatially extended sources
 with extensions varying from
$~0.1\deg$ to $~0.25\deg$ (\cite{hess_plane_survey}). In fact, within
our Galaxy only very few sources (most notably the $\gamma$-ray binaries
LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI})
and HESS\,J0632+057 (\cite{HESS0632}) are amongst the few Galactic sources
for which no significant extension was detected at \tev energies. Given
these findings, it can be expected that if the source population at \gev
energies has similar properties, that at least some of the Fermi-LAT
sources in our Galaxy should be spatially resolvable at \gev energies.

@@

@@

\todo[inline]{Add interpretations of Puppis A.}

@@

2FGL reported on the detection of twelve spatially extended sources. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to identify the LAT source. Even still, for many extended LAT
sources the source class and emission process is still uncertain.

The position of the 21 extended LAT sources is plotted in
figure~\ref{allsky_extended_sources}.  Most of them lie along the galactic
plane.  This is expected because extragalactic sources are typically too
far away to be resolvable and most Galactic sources lie along the plane.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
     The plot shows the null distribution of
    the likelihood ratio test when fitting a point source for extension.
    The $x$ axis is \tsext and the $y$ axis is the cumulative density
    for \tsext of simulated point sources. The four plots represent
    different spectral indices and the different colors represent
    different fluxes.  The dashed red line is the cumulative density
    function of $\chi^2(\ts)/2$ which is suggested by Wilks' theorem
    as the distribution these curves should should follow.  There is
    good agreement between the Monte Carlo results and
    the theoretical distribution. For most spectral parameters, the
    Monte Carlo curve lies to the left of the theoretical curve which
    would make the theoretical distribution more conservative.  In this
    paper, we use this theoretical curve to estimate the significance of
    the detection of a source's extension. This plot cuts off 
    three simulations with $\tsext>25$. They 
    had a flux $3\times10^{-8}\ph/\cm^2/\sec$, spectral index
    2.5, and \tsext of 26.1, 28.9, and 38.1.
    The Monte Carlo simulation is described in 
    section \ref{monte_carlo_validation} and 
    the number of simulation for each spectral model 
    are presented in table~\ref{ts_ext_num_sims}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \end{center}
    \caption{
    This plot shows the detection threshold to resolve a uniform
    disk extended source.  The detection threshold is defined as the flux where
    $\langle\tsext\rangle=16$ for a given extension.  The $x$ axis is
    the extension of a uniform disk extended source and the $y$ axis
    is the source's 100 \mev to 100 \gev photon flux.  All sources have
    an assumed power-law spectrum and the different colors are different
    simulated spectral indices.  The solid line is the detection threshold
    using photons with energy between 100 \mev and 100 \gev while the
    dashed line is the threshold using 1-100 \gev photons. The detection threshold is for the same two year time
    range as was used in 2FGL and in the following extended source search.
    The extended sources are simulated against
  a Sreekumar-like isotropic background.  More information
    about this plot is presented in section~\ref{extension_sensitivity}.
    This plot shows that our threshold to detecting the extension of
    a source is best for a source with size $~0.5\deg$. It also shows
    that for sources neither too large nor soft, our sensitivity is not
    significantly improved using photons with energy between 100 \mev
    and 1 \gev. More information about this plot is presented
    in section~\ref{extension_sensitivity}.
    }\label{index_sensitivity}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
    \end{center}
    \caption{
    This shows the detection threshold to a uniform disk extended
    source for varying background levels
    and energy ranges.  The plots have the same meaning as in
    figure~\ref{index_sensitivity} and the simulations occur over the
    same time range.  The solid blue line is the detection threshold against a
    Sreekumar-like isotropic background. The green dashed curve is the
    threshold against 10 times the isotropic background and the dash
    dotted red curve is the threshold against 100 times the isotropic
    background.  The latter factor approximately represents the intensity
    of the Galactic diffuse emission near the Galactic center.  Plot (a)
    is the threshold using 1-100\gev photons while plot (b) is the threshold using
    10-100\gev photons. Unlike figure~\ref{index_sensitivity},
    the detection threshold was calculated only for a power-law source of spectral
    index 2. The flux is quoted only in the selected energy range which
    weakens the dependence of the detection threshold on spectral index.
    These plots show that we are less sensitive to extended sources in
    regions with higher background and (given the same number of photons)
    more sensitive to harder sources.  Overlaid on this plot are the
    extended sources found in this extended source search. The extended
    sources are color coded based upon whether the integral galactic
    diffuse and isotropic diffuse emission model is closer to 1x, 10x,
    or 100x the Sreekumar-like isotropic spectrum.  The red point
    in plot (a) below the red line is RX J1713.7-3946 which is harder
    ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
    than the isotropic emission.  The green point in plot (b) below
    the green line is MSH 15-52 which was found by our analysis to
    have $\tsext=6.5$.  More information about this plot is presented
    in section~\ref{extension_sensitivity}.
    }\label{diff_factor_sensitivity}
  \end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/time_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
    \end{center}
    \caption{
    This plot shows our projected sensitivity to extension after 10 years
    of operation for an assumed power-law source of spectral index
    2 against a representative 10 times the isotropic background in the
    energy range from 1-100 \gev (solid red) and 10-100 \gev (dashed
    blue). Flux is quoted in this energy range and the gray region is
    the projected detection threshold to the extension
  of a source assuming that it improves
    from the 2 year threshold
    with $\sqrt{\text{t}}$ (top edge) and linearly with time (bottom
    edge). For small extended sources, our detection threshold to the extension
    of a source actually improves better than $\sqrt{\text{t}}$
    because at the highest energies, where we are most sensitive to the
    extension of a source, the relevant background near the sources is in
    the Poisson instead of Gaussian regime.  For large extended sources,
    the relevant background is over a larger area and our gain
    improvement is closer to $\sqrt{\text{t}}$.  This effect is
    even more pronounced for sources hard only above 10 \gev.
    }\label{time_sensitivity}
  \end{figure}

@@

\clearpage
\thispagestyle{empty}
\begin{sidewaystable}
  \begin{centering}
    \begin{tabular}{l|rrlrrrrrrr}
      \hline
      \hline
      Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index &          Counterpart \\
      \hline
      \multicolumn{10}{c}{$E > 1 \gev$} \\
      \hline
      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg \pm   0.02\deg $ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg \pm   0.02\deg $ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg \pm   0.01\deg $ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
      \hline
      \multicolumn{10}{c}{$E > 10 \gev$} \\
      \hline
      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg \pm   0.05\deg $ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg \pm   0.01\deg $ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg \pm   0.01\deg $ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg \pm   0.03\deg $ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg \pm   0.03\deg $ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg \pm   0.02\deg $ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
      \hline
  \end{tabular}
    \caption{The 8 new source candidates found by the extended source
    search. Three new extended sources were found using photons with
    energies above 1 \gev and five new candidates were found using
    photons with energies above 10 \gev.  The columns in this table
    have the same meaning as in table~\ref{known_extended_sources}.
    More information about these sources can be found in
    section~\ref{new_ext_srcs_section}.
    }
    \label{new_ext_srcs_table}
  \end{centering}
\end{sidewaystable}

@@

  \clearpage
\begin{appendices}

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/all_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \end{center}
    \caption{These six plots condense the LAT detection threshold for
    all four spectral indices shown in figure~\ref{index_sensitivity}
    (1.5, 2, 2.5, and 3) and all three background levels shown
    in~\ref{diff_factor_sensitivity}.  (1x, 10x, and 100x the
    Sreekumar-like isotropic spectrum).  The plots have the same meaning
    as in figure~\ref{index_sensitivity} The left plots are the detection
    threshold when using 1-100 \gev photons and the right plots are the detection threshold when using
    10-100 \gev photons.  This plot shows
    that when using only high energy photons with an improved angular
    resolution, our detection threshold is only weakly a function of
    spectral index. The numeric values plotted here are tabulated
    in table~\ref{all_sensitivity_table}. More information about this plot is presented
    in section~\ref{extension_sensitivity}.
    }\label{all_sensitivity} 
  \end{figure}
      table is when using 10-100 \gev photons. The first column is
      source assuming a uniform surface brightness. The table quotes fluxes in units of
      $10^{-10} \ph/\cm^2/\sec$.  These values are also plotted in
      figure~\ref{all_sensitivity}.  More information about this
      table is presented in section~\ref{extension_sensitivity}.

\end{appendices}

>>>>

\usepackage[textwidth=0.8in,colorinlistoftodos]{todonotes}

@@

\todo[inline]{Remove from all figures - "more infomration can be foudn in"}

@@

For each of these sources, the extension was determined based on
dedicated analysis of the particular source or region of interest
instead of being the outcome of a systematic search of the LAT catalog.
For the systematic scan of all LAT catalog sources presented here, we
therefore expect to find additional spatially extended LAT sources, in
particular since many extended sources in the Galactic plane have been
detected at \tev energies using Air Cherenkov detectors and \tev and
\gev emission often originates from the same population of high-energy
particles.  A variety of spatially extended sources have been detected
in the Galactic plane at \tev energies. Most prominent was a survey of
the Galactic plane using the High Energy Stereoscopic System (H.E.S.S)
which presented 14 spatially extended sources
 with extensions varying from
$~0.1\deg$ to $~0.25\deg$ (\cite{hess_plane_survey}). In fact, within
our Galaxy only very few sources (most notably the $\gamma$-ray binaries
LS\,5039 (\cite{HESSLS5039}), LS I+61-303 (\cite{MAGICLSI, VERITASLSI})
HESS\,J0632+057 (\cite{HESS0632}), and the Crab nebula (\cite{crab_weekes})
are amongst the few Galactic sources
for which no significant extension was detected at \tev energies. Given
these findings, it can be expected that if the source population at \gev
energies has similar properties, that at least some of the Fermi-LAT
sources in our Galaxy should be spatially resolvable at \gev energies.

@@

todo[inline]{This text needs to be fixed}

@@

\todo[inline]{Add interpretations of Puppis A.}
\todo[inline]{Markus says to add an SED.}

@@

2FGL reported on the detection of twelve sources
prviously known as extende. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to firmly associate the LAT source in many cases.

The position of the 21 extended LAT sources are close to the Galactic
plane and plotted in figure~\ref{allsky_extended_sources}.  Most of the
extended sources are indeed expected to be of Galactic origin as the
distance of extragalactic sources (with exception of the local group
Galaxies) is typically too large to resolve them in gamma rays.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/ts_ext_emin_1000.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/ts_ext/v3/plot.py
    % using data from /nfs/slac/g/ki/ki03/lande/extended_catalog/monte_carlo/ts_ext/v3_emin_1000/merged.hdf5
    \end{center}
    \caption{
    Distribution of the test statistic \tsext of a likelihood ratio
    test when fitting the extension of a point source.  The four plots
    represent simulated point sources of different spectral indices and
    the different colors represent point sources with different 100 \mev
    to 100 \gev integral fluxes.  The dashed red line is the cumulative
    density function of equation~\ref{ts_ext_distribution}.
    }\label{ts_ext_mc}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/index_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_index.py
    \end{center}
    \caption{
    The detection threshold ($\langle\tsext\rangle=16$) to resolve a
    uniform disk extended source for a two-year exposure.  All sources
    have an assumed power-law spectrum and the different colors correspond
    to different simulated spectral indices.  The solid line is the
    detection threshold using photons with energy between 100 \mev and 100
    \gev while the dashed line is the threshold using 1-100 \gev photons.
    }\label{index_sensitivity}
  \end{figure}

@@

% \begin{figure}
%   \begin{center}
%     \includegraphics{mc_plots/diff_factor_sensitivity.pdf}
%     % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_diff_factor.py
%     \end{center}
%     \caption{
%     This shows the detection threshold to a uniform disk extended
%     source for varying background levels
%     and energy ranges.  The plots have the same meaning as in
%     figure~\ref{index_sensitivity} and the simulations occur over the
%     same time range.  The solid blue line is the detection threshold against a
%     Sreekumar-like isotropic background. The green dashed curve is the
%     threshold against 10 times the isotropic background and the dash
%     dotted red curve is the threshold against 100 times the isotropic
%     background.  The latter factor approximately represents the intensity
%     of the Galactic diffuse emission near the Galactic center.  Plot (a)
%     is the threshold using 1-100\gev photons while plot (b) is the threshold using
%     10-100\gev photons. Unlike figure~\ref{index_sensitivity},
%     the detection threshold was calculated only for a power-law source of spectral
%     index 2. The flux is quoted only in the selected energy range which
%     weakens the dependence of the detection threshold on spectral index.
%     These plots show that we are less sensitive to extended sources in
%     regions with higher background and (given the same number of photons)
%     more sensitive to harder sources.  Overlaid on this plot are the
%     extended sources found in this extended source search. The extended
%     sources are color coded based upon whether the integral galactic
%     diffuse and isotropic diffuse emission model is closer to 1x, 10x,
%     or 100x the Sreekumar-like isotropic spectrum.  The red point
%     in plot (a) below the red line is RX J1713.7-3946 which is harder
%     ($\gamma\approx1.5$) and has diffuse emission only 53 times larger
%     than the isotropic emission.  The green point in plot (b) below
%     the green line is MSH 15-52 which was found by our analysis to
%     have $\tsext=6.5$.  More information about this plot is presented
%     in section~\ref{extension_sensitivity}.
%     }\label{diff_factor_sensitivity}
%   \end{figure}

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/all_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_all.py
    \end{center}
    \caption{the LAT detection threshold for four spectral indices and
    three background (1x, 10x, and 100x the Sreekumar-like isotropic
    spectrum) for a two-year exposure. The left plots are the detection
    threshold when using 1-100 \gev photons and the right plots are
    the detection threshold when using 10-100 \gev photons.  The flux
    is integrated only in the selected energy range.  Overlaid on this
    plot are the LAT detected extended sources placed by the nearby
    Galactic diffuse emission and color coded by their spectral idnex.
    The black point in plot (d) below the green line is MSH 15-52 which
    was found by our analysis to have $\tsext=6.5$.  
    }\label{all_sensitivity} 
  \end{figure}
      table when using 10-100 \gev photons. The first column is
      source assuming a uniform surface brightness. The table quotes integral
      fluxes in the analyzed energy range in units of
      $10^{-10} \ph/\cm^2/\sec$.  

\begin{figure}
  \begin{center}
    \includegraphics{mc_plots/time_sensitivity.pdf}
    % this plot came from /u/gl/lande/work/fermi/extended_catalog/monte_carlo/sensitivity/v12/plot/plot_vs_time.py
    \end{center}
    \caption{
    Our projected sensitivity to extension after 10 years for a power-law
    source of spectral index 2 against 10 times the isotropic background
    in the energy range from 1-100 \gev (solid red) and 10-100 \gev
    (dashed blue). This background is representative of the background
    near the Galactic plane.  The solid gray region is the projected
    detection threshold assuming the sensitivity improves from the 2
    year threshold by $\sqrt{\text{t}}$ (top edge) and linearly with
    time (bottom edge).  The lower plot shows the factor increase in
    sensitivity.  For small extended sources, our detection threshold
    improves better than $\sqrt{\text{t}}$ because at high energies where
    we are most sensitive to extension, the background levels are in the
    Poisson instead of Gaussian regime.  For large extended sources,
    the relevant background is larger and the improvement is closer
    to $\sqrt{\text{t}}$.
    }\label{time_sensitivity}
  \end{figure}

@@

\clearpage
\thispagestyle{empty}
\begin{sidewaystable}
  \begin{centering}
    \begin{tabular}{l|rrlrrrrrrr}
      \hline
      \hline
      Name                 &          \glon &          \glat &                \multicolumn{1}{r}{$\sigma$} &         TS &   $\tsext$ &    Pos Err &                  Flux &                 Index &          Counterpart \\
      \hline
      \multicolumn{10}{c}{$E > 1 \gev$} \\
      \hline
      2FGL\,J0823.0-4246   &     260.32\deg &      -3.28\deg & $  0.37\deg \pm   0.03\deg \pm   0.02\deg $ &      320.9 &       46.3 &   0.02\deg & $    8.5 \pm     0.7$ & $   2.20 \pm    0.09$ &             Puppis A \\
      2FGL\,J1627.0-2425c  &     353.08\deg &      16.78\deg & $  0.41\deg \pm   0.05\deg \pm   0.02\deg $ &      144.5 &       31.1 &   0.04\deg & $    6.5 \pm     0.6$ & $   2.49 \pm    0.14$ &            Ophiuchus \\
      2FGL\,J1712.4-3941   &     347.25\deg &      -0.54\deg & $  0.56\deg \pm   0.04\deg \pm   0.01\deg $ &       75.0 &       39.6 &   0.05\deg & $    4.2 \pm     0.9$ & $   1.47 \pm    0.12$ &     RX\,J1713.7-3946 \\
      \hline
      \multicolumn{10}{c}{$E > 10 \gev$} \\
      \hline
      2FGL\,J0851.7-4635   &     266.29\deg &      -1.43\deg & $  1.13\deg \pm   0.08\deg \pm   0.05\deg $ &      116.1 &       87.2 &   0.07\deg & $    1.3 \pm     0.2$ & $   1.76 \pm    0.21$ &             Vela Jr. \\
      2FGL\,J1615.0-5051   &     332.38\deg &      -0.14\deg & $  0.33\deg \pm   0.04\deg \pm   0.01\deg $ &       53.4 &       16.3 &   0.04\deg & $    1.1 \pm     0.2$ & $   2.24 \pm    0.28$ &      HESS\,J1616-508 \\
      2FGL\,J1615.2-5138   &     331.66\deg &      -0.66\deg & $  0.42\deg \pm   0.03\deg \pm   0.01\deg $ &       76.6 &       48.0 &   0.05\deg & $    1.2 \pm     0.2$ & $   1.77 \pm    0.24$ &      HESS\,J1614-518 \\
      2FGL\,J1632.4-4753c  &     336.41\deg &       0.22\deg & $  0.44\deg \pm   0.04\deg \pm   0.03\deg $ &      127.8 &       64.5 &   0.04\deg & $    1.9 \pm     0.2$ & $   2.29 \pm    0.21$ &      HESS\,J1632-478 \\
      2FGL\,J1837.3-0700c  &      25.08\deg &       0.13\deg & $  0.35\deg \pm   0.08\deg \pm   0.03\deg $ &       46.2 &       18.8 &   0.07\deg & $    1.0 \pm     0.2$ & $   1.63 \pm    0.29$ &      HESS\,J1837-069 \\
      2FGL\,J2021.5+4026   &      78.18\deg &       2.19\deg & $  0.59\deg \pm   0.03\deg \pm   0.02\deg $ &      222.2 &      116.4 &   0.04\deg & $    1.8 \pm     0.2$ & $   2.31 \pm    0.19$ &          Gamma Cygni \\
      \hline
  \end{tabular}
    \caption{The 9 new source candidates found by the extended source
    search. Three new extended sources were found using photons with
    energies above 1 \gev and five new candidates were found using
    photons with energies above 10 \gev.  The columns in this table
    have the same meaning as in table~\ref{known_extended_sources}.
    More information about these sources can be found in
    section~\ref{new_ext_srcs_section}.
    }
    \label{new_ext_srcs_table}
  \end{centering}
\end{sidewaystable}

@@
